\documentclass[10pt]{article}
\usepackage{newcent}   % uses new century schoolbook postscript font 

\usepackage{geometry}
\geometry{
a4paper,
total={170mm,257mm},
left=20mm,
top=20mm,
headheight=0pt
}

\usepackage[dvipsnames]{xcolor}
\usepackage{array}
\usepackage[unicode=true,colorlinks=true,urlcolor=CadetBlue,citecolor=black,linkcolor=black]{hyperref}
\usepackage{longtable}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt} %no extra line break above or between itemized entries

% Customization
\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

% Header
\usepackage{fancyhdr}
\usepackage{lastpage}

\pagestyle{fancy}
\lhead{Yoav Ram | CV}
\cfoot{}
\rhead{\thepage\ / \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\fancypagestyle{plain}{%
\fancyhf{} % clear all header and footer fields
\fancyhead[r]{\thepage\ / \pageref{LastPage}} % except the center
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}}

\begin{document}

\thispagestyle{plain} % no header on first page

\begin{center}
{\huge\bf Yoav Ram | CV} \\
\smallskip
{\large School of Computer Science,
IDC Herzliya} \\
\smallskip
{\small 
yoav.ram@idc.ac.il \quad
www.yoavram.com \quad
+972 (545) 383136
}
\end{center} 

\vspace{\baselineskip} \hrule height 1pt \vspace{0.5\baselineskip}

\section*{Education} {
\begin{longtable}{L!{\VRule}R}

2010-2016 & 
\textbf{Ph.D.}, Direct Ph.D. track, Tel Aviv University \\
& Thesis title: \emph{The Evolution of Stress-Induced Mutagenesis: Causes and Consequences} \\
\\
2010-2012 & 
\textbf{M.Sc.}, Direct Ph.D. track, Tel Aviv University \\
& Theoretical and Computational Biology \\
\\
2007-2010 & 
\textbf{B.Sc.}, Biology and Mathematics \emph{magna cum lauda}, Tel Aviv University \\

\end{longtable}
}  

%\pagebreak

\section*{Employment} {
\begin{longtable}{L!{\VRule}R}

2018- &
\textbf{Senior lecturer}, Efi Arazi School of Computer Science, Interdisciplinary Center Herzliya \\
\\
2016-2018 &
\textbf{Postdoctoral fellow}, Center for Computational, Evolutionary, and Human Genomics, Stanford University \\
& Mentor | Prof. Marcus W. Feldman, Department of Biology  \\
\\
2016 & 
\textbf{Postdoctoral fellow}, Hadany Lab, Tel Aviv University \\
& Mentor | Prof. Lilach Hadany, Department of Plant Sciences  \\
\\
2016 & 
\textbf{Data scientist }, Neura \\
\\
2010-2016 & 
\textbf{Ph.D. student}, Hadany Lab, Tel Aviv University \\
& Mentor | Prof. Lilach Hadany, Department of Plant Sciences  \\
\\
2008-2010 & 
\textbf{Research assistant}, Hadany Lab, Tel Aviv University \\
& Mentor | Prof. Lilach Hadany, Department of Plant Sciences  \\
\\
2008-2009 & 
\textbf{Software developer}, NetAlign \\
\\
2006-2008 & 
\textbf{Software developer}, XLNet \\
\\
%2002-2006 & 
%\textbf{Communications researcher}, IDF Intelligence Corps \\
%\\

\end{longtable}
}  

\pagebreak

\section*{Grants \& Awards} {
\begin{longtable}{L!{\VRule}R}

2020 & \textbf{Israel Science Foundation} (ISF) KillCorona research grant, 2020-2022 \\*
$\ast$ & \textbf{John Templeton Foundation} grant, Co-PI (with MW~Feldman, Stanford; K~Laland, St.~Andrews), 2021-2024 \\*
$\ast$ & \textbf{Minerva}  Center on Lab Evolution, Co-PI (head: Y Pilpel, WIS), 2020-2025 \\*
\\*
2019 & \textbf{Israel Science Foundation} (ISF) Personal Research grant, 2019-23 \\*
$\ast$ & \textbf{AWS} Cloud Credits for Research program \\*
$\ast$ & \textbf{NVIDIA} Accelerated Data Science GPU grant \\*
\\*
2016-17 & \textbf{Postdoctoral fellowship} from the Stanford Center for Computational, Evolutionary, and Human Genomics \\*
\\*
2015-16 & \textbf{Dean's Award for Excellence in Teaching}, Engineering Faculty, Tel Aviv University \\*
\\*
2015 & The Israel Society for Microbiology travel award \\*[0.1cm]
$\ast$ & The Anat Karuskopf Fund travel award \\*[0.1cm]
$\ast$ & The Manna Institute for Plants BioSciences travel award \\*
\\*
2014 & The Israeli Ministry of Science and Technology \textbf{International Education Scholarship} \\*
\\
2013-2014 & Research achievements scholarship, Life Sciences Faculty, Tel Aviv University. \\*[0.1cm]
$\ast$ & Fellowship from the Manna Program in Food Safety and Security \\*
\\
2013 & The Manna Institute for Plants BioSciences travel award \\*
\\
2012 & Registration \& accommodation waiver for PopGroup45 in Nottingham, UK \\*[0.1cm]
$\ast$ & Crowd-funded travel expenses for PopGroup45 via The \#SciFund Challenge \\*
\\
2011-2012 & Research achievements scholarship, Life Sciences Faculty, Tel Aviv University \\*
\\
2011 & Society for the Study of Evolution International travel award \\*
\\
2010-2015 & \textbf{Direct Ph.D. scholarship}, Department of Plant Sciences, Tel Aviv University \\*
\\
2010 & Society for Molecular Biology \& Evolution Undergraduate Diversity Mentoring Program award \\*[0.1cm]
$\ast$ & \textbf{Best poster award} at Mathematical Methods in Systems Biology workshop, Tel Aviv, Israel \\*
\\
2009 & Amos de-Shalit Ulpana for excellent students in Life Sciences, Weizmann Institute. \\*
\end{longtable}
} 

\pagebreak

\section*{Publications
{\small\sl$^*$equal contribution $|$ citation counts from \href{https://scholar.google.com/citations?user=RIFmJvYAAAAJ}{Scholar}}} {
\begin{longtable}{L!{\VRule}R}

%%%%%%%%%%%
\textbf{Preprints}
%%%%%%%%%%%
& Kohanovski, I., Obolski, U., \textbf{Ram, Y.} (2020) \emph{Inferring the effective start dates of non-pharmaceutical interventions during COVID-19 outbreaks}. medRxiv. DOI: \href{http://doi.org/10.1101/2020.05.24.20092817}{10.1101/2020.05.24.20092817} \\*
\\
& Arthur, R.F., Jones, J.H., Bonds, M.H., \textbf{Ram, Y.}, Feldman, M.W. \emph{Adaptive social contact rates induce complex dynamics during epidemics}. bioRxiv. DOI: \href{http://doi.org/10.1101/2020.04.14.028407}{10.1101/2020.04.14.028407} \\*
\\
& Cohen, O., \textbf{Ram, Y.}, Hadany, L., Gafny, S., Geffen, E. \emph{Annual climatic fluctuations and short-term variations in population genetics}. Submitted. \\*
\\

%%%%%%%%%%%
\textbf{Published} 
%%%%%%%%%%%
& Kolodny, O., Berger, M.,  Feldman, M.W., \textbf{Ram, Y.} (2020) \emph{A new perspective for mitigation of SARS-CoV-2 infection: priming the immune system for attack}. Open Biology. DOI: \href{http://doi.org/10.1098/rsob.200138}{10.1098/rsob.200138} \\*
\\
& Krebs Denton, K., \textbf{Ram, Y.}, Liberman, U., Feldman, M.W. (2020) \emph{Cultural evolution of conformity and anticonformity}. Proceedings of the National Academy of Sciences USA. DOI: \href{http://doi.org/10.1073/pnas.2004102117}{10.1073/pnas.2004102117} \\*
\\
& \textbf{Ram, Y.}, Obolski, U., Feldman, M.W., Berman, J. and Hadany, L. (2020) \emph{Reply to Balsa-Canto et al.: Growth models are applicable to growth data, not to stationary-phase data}. Proceedings of the National Academy of Sciences USA. DOI: \href{http://doi.org/10.1073/pnas.1917758117}{10.1073/pnas.1917758117} \\*
\\
& Liberman, U., \textbf{Ram, Y.}, Altenberg, L., Feldman, M.W. \emph{The Evolution of Frequency-Dependent Cultural Transmission}. Theoretical Population Biology. DOI: \href{http://doi.org/10.1016/j.tpb.2019.12.004}{10.1016/j.tpb.2019.12.004} \\*
\\
& \textbf{Ram, Y.}, Dellus-Gur, E., Bibi, M., Karkare, K., Obolski, U., Feldman, M.W., Cooper, T.F., Berman, J. and Hadany, L. (2019) \emph{Predicting Microbial Growth in a Mixed Culture from Growth Curve Data}. Proceedings of the National Academy of Sciences USA, 201902217. DOI: \href{https://doi.org/10.1073/pnas.1902217116}{10.1073/pnas.1902217116}. \\*
\\
& \textbf{Ram, Y.}, Hadany, L. (2019) \emph{Evolution of stress-induced mutagenesis in the presence of horizontal gene transfer}. The American Naturalist, 194:1. DOI: \href{http://doi.org/10.1086/703457}{10.1086/703457}. \\*
\\
& Zinger, E., Guiejman, A, Obolski, U., \textbf{Ram, Y.}, Ruby, E., Binder, M., Yechieli, N., Ohad, N., Hadany L. (2019) \emph{Less fit \emph{Lamium amplexicaule} plants produce more dispersible seeds}. Scientific Reports, Accepted. DOI: \href{http://doi.org/10.1038/s41598-019-42158-1}{10.1038/s41598-019-42158-1}. \\*
\\
& \textbf{Ram, Y.}, Liberman, U., Feldman, M.W. (2019) \emph{Vertical and oblique cultural transmission fluctuating in time and in space}. Theoretical Population Biology, 125:11-19. DOI: \href{http://doi.org/10.1016/j.tpb.2018.11.001}{10.1016/j.tpb.2018.11.001}. \\*
\\
& \textbf{Ram, Y.}, Liberman, U., Feldman, M.W. (2018) \emph{Evolution of vertical and oblique transmission under fluctuating selection}. Proceedings of the National Academy of Sciences USA, 201719171. DOI: \href{http://doi.org/10.1073/pnas.1719171115}{10.1073/pnas.1719171115}. \\*
\\
& \textbf{Ram, Y.}, Altenberg, L., Liberman, U., Feldman, M.W. (2018) \emph{Generation of variation and a modified mean fitness principle: Necessity is the mother of genetic invention}. Theoretical Population Biology, 123:1-8. DOI: \href{https://doi.org/10.1016/j.tpb.2018.02.004}{10.1016/j.tpb.2018.02.004}. \\*
\\
& Harari, Y., \textbf{Ram, Y.}, Rappoport, N., Hadany, L., Kupiec, M. (2018) \emph{Spontaneous changes in ploidy are common in yeast}. Current Biology, 28:1–11. DOI: \href{https://doi.org/10.1016/j.cub.2018.01.062}{j.cub.2018.01.062}. 4 citations \\ *
\\
& Harari, Y., \textbf{Ram, Y.}, Kupiec, M. (2018) \emph{Frequent ploidy changes in growing yeast cultures}. Current Genetics, 0:1–4.. DOI: \href{https://doi.org/10.1007/s00294-018-0823-y}{10.1007/s00294-018-0823-y}. 1 citation \\ *
\\
& Obolski, U.$^*$, \textbf{Ram, Y.}$^*$, Hadany, L. (2018) \emph{Evolution on rugged adaptive landscapes}. Reports on Progress in Physics, 81: 12602. DOI: \href{http://doi.org/10.1088/1361-6633/aa94d4}{10.1088/1361-6633/aa94d4}. 2 citations \\*
\\
& Dellus-Gur, E., \textbf{Ram, Y.}, Hadany, L. (2017) \emph{Errors in mutagenesis and the benefit of cell-to-cell signalling in the evolution of stress-induced mutagenesis}. Royal Society Open Science, 4:170529. DOI: \href{http://doi.org/10.1098/rsos.170529}{10.1098/rsos.170529}. 1 citation \\*
\\
& Obolski, U., Lewin-Epstein, O., Even-Tov, E., \textbf{Ram, Y.}, Hadany, L. (2017) \emph{With a little help from my friends: cooperation can accelerate the rate of adaptive valley crossing}. BMC Evolutionary Biology, 17:143. DOI: \href{http://doi.org/10.1186/s12862-017-0983-2}{10.1186/s12862-017-0983-2}. 2 citations \\*
\\
& Rougier, N.P., $\ldots$ , \textbf{Ram, Y.}, et al. (2017) \emph{Sustainable computational science: the ReScience initiative}. PeerJ Computer Science, 3: e142. DOI:\href{http:/doi.org/10.7717/peerj-cs.142}{10.7717/peerj-cs.142}. 11 citations \\*
\\
& \textbf{Ram, Y.}, Hadany, L. (2016) \emph{Condition-dependent sex: who does it, when, and why?}. Philosophical Transactions of the Royal Society B, 371: 20150539. DOI: \href{http://doi.org/10.1098/rstb.2015.0539}{10.1098/rstb.2015.0539}. 14 citations \\
\\
& \textbf{Ram, Y.}, Hadany, L. (2015) \emph{The probability of improvement in Fisher's geometric model: a probabilistic approach}. Theoretical Population Biology, 99: 1-6. DOI: \href{http://doi.org/10.1016/j.tpb.2014.10.004}{10.1016/j.tpb.2014.10.004}. 5 citations \\
\\
& \textbf{Ram, Y.}, Hadany, L. (2014) \emph{Stress-induced mutagenesis and complex adaptation}. Proceedings of the Royal Society B. 281: 20141025. DOI: \href{http://doi.org/10.1098/rspb.2014.1025}{10.1098/rspb.2014.1025}. 33 citations \\
\\
& Gueijman, A., Ayali, A., \textbf{Ram, Y.}, Hadany, L. (2013) \emph{Dispersing away from bad environments: The evolution of fitness-associated dispersal (FAD) in homogeneous environments}. BMC Evolutionary Biology, 13:125. DOI: \href{http://doi.org/10.1186/1471-2148-13-125}{10.1186/1471-2148-13-125}. 15 citations \\
\\
& \textbf{Ram, Y.}, Hadany, L. (2012) \emph{The evolution of stress-induced hypermutation in asexual populations}. Evolution 66: 2315-2328. DOI: \href{http://doi.org/10.1111/j.1558-5646.2012.01576.x}{10.1111/j.1558-5646.2012.01576.x}. 55 citations \\
\\
%%%%%%%%%%%
%\textbf{Submitted}
%%%%%%%%%%%

%\\

%\pagebreak

%%%%%%%%%%%
\textbf{Datasets \\ \& Software}
%%%%%%%%%%%
& \textbf{Ram, Y.}, Hadany, L. (2019) \emph{Data from: Evolution of Stress-Induced Mutagenesis in the Presence of Horizontal Gene Transfer}. Dryad Digital Repository. DOI:\href{http://doi.org/10.5061/dryad.5t9211b}{10.5061/dryad.5t9211b}. \\
\\
& \textbf{Ram, Y.}, Hadany, L. (2019) \emph{Curveball: Predicting microbial growth in a mixed culture from growth curve data}. Zenodo. \href{http://doi.org/10.5281/zenodo.3263379}{10.5281/zenodo.3263379}. \\
\\
& \textbf{Ram, Y.}, Hadany, L. (2019) \emph{Mamba: Version Baptiste}. Zenodo. \href{http://doi.org/10.5281/zenodo.2563549}{10.5281/zenodo.2563549}. \\
\\
& \textbf{Ram, Y.}, Zinger, E., Hadany, L. (2017) \emph{Sid: Image processing for seed images}. Zenodo. DOI: \href{http://doi.org/10.5281/zenodo.344898}{10.5281/zenodo.344898}. \\
\\
& \textbf{Ram, Y.}, Hadany L. (2014) \emph{Data from: Stress-induced mutagenesis and complex adaptation}. Dryad Digital Repository. DOI: \href{http://doi.org/10.5061/dryad.3066j}{10.5061/dryad.3066j}. \\
\\
& \textbf{Ram, Y.}, Guiejman, A. and Hadany L. (2014) \emph{proevolution simulation: Version Dobzhansky}. ZENODO. DOI: \href{http://doi.org/10.5281/zenodo.11400}{10.5281/zenodo.11400}. \\
\\
& \textbf{Ram, Y.}, Hadany, L. (2014) \emph{proevolution simulation: Version Charles. ZENODO}. DOI: \href{http://doi.org/10.5281/zenodo.11401}{10.5281/zenodo.11401}.\\

\end{longtable}
} 

%\pagebreak

\section*{Teaching \& Mentoring Experience} {
\begin{longtable}{L!{\VRule}R}

2018-- &
\textbf{Senior Lecturer}, IDC Herzliya \\*
& Introduction to Computer Science (undergraduate mandatory course) \\*
& Scientific Computing with Python (advanced course) \\*
& Computational Models in Biology (graduate seminar) \\*
\\
2016-- &
\textbf{Technical Instructor}, Industry \\*
& Designed and developed multiple scientific programming workshops \\*
& Taught 1-5 day workshops in Israel and in California \\*
& \href{http://python.yoavram.com}{python.yoavram.com} \\*
\\
2013-2015 & 
\textbf{Lecturer}, Tel Aviv University \\*
& Python Programming for Engineers (Engineering Faculty) \\*
& Python Programming for Biologists (Life Sciences Faculty) \\*
& Introduction to Programming for Engineers (summer introductory course) \\*
& Gentle Introduction to Programming (summer introductory course) \\*
\\
2013-2016 &
\textbf{Mentoring} of undergraduate and graduate students at Hadany Lab \\*
& Supervised five undergraduate students doing research projects \\*
& Participated in mentoring of three postgraduate students \\*
\\
2011-2015 & 
\textbf{Teaching Assistant}, Python Programming for Engineers, Tel Aviv University \\*
& Python Programming for Engineers (Engineering Faculty) \\*
& Extended Introduction to Computer Science (School of Computer Science) \\*
& Evolution (Life Sciences Faculty) \\*
%2010-2012 &
%\textbf{Private Teacher}, undergraduate Mathematics and Computer Science students \\*
%\\
%2005 & 
%\textbf{Course Commander}, IDF Intelligence Corps \\*
%& Responsible for intensive 3-month training of 8 recruits with B.Sc. in Exact Sciences \\*
ֿֿ
\end{longtable}
}  

%\pagebreak

\section*{Selected Presentations} {
\begin{longtable}{L!{\VRule}R}
2020
& Invited speaker, \emph{TAU Theory-fest} (Evolution workshop), Tel Aviv University \\*[0.1cm]
$\ast$ & Invited speaker, \emph{The Language of Evolution \& Evolution of Language} conference, Weizmann Institute \\*[0.1cm]
$\ast$ & Oral presentation, \emph{FISEB/ILANIT}, Eilat. \\*[0.1cm]
\\
2019
& Oral presentation, \textbf{\emph{Gordon Research Conference}} on Molecular Mechanisms in Evolution, Stonehill College, Easton, MA, USA \\*[0.1cm]
$\ast$ & Oral presentation, \emph{Israel Society for Microbiology} annual meeting, Weizmann Institute \\*[0.1cm]
$\ast$ & Oral presentation, \emph{Socio-Technological Evolution of the Human Species} workshop, Safed, Israel \\*[0.1cm]
$\ast$ & Seminar, \emph{Center for Genomics and Systems Biology}, New York University, New York \\*[0.1cm]
$\ast$ & Session chair \& Oral presentation, the \textbf{\emph{First Meeting of the Israeli Society for Evolutionary Biology}}, Steinhardt Museum of Natural History, Tel Aviv \\*[0.1cm]
$\ast$ & Poster presentation by student, the \emph{First Meeting of the Israeli Society for Evolutionary Biology}, Steinhardt Museum of Natural History, Tel Aviv \\*[0.1cm]
$\ast$ & Poster presentation by student, \emph{Genetics, Genomics \& Evolution}, Tel Aviv University \\*[0.1cm]
\\
2018
& Invited speaker, \emph{Genome Evolution Conference}, Weizmann Institute \\*[0.1cm]
\\
2017 
& Oral presentation, \emph{Evolgenome} seminar, Stanford University \\*[0.1cm]
$\ast$ & Poster, \emph{Gordon Research Conference} on Biological Mechanisms in Evolution, Stonehill College, Easton, MA, USA \\*[0.1cm]
$\ast$ & Oral presentation, \emph{Israel Society for Microbiology} annual meeting. \\*[0.1cm]
$\ast$ & Oral presentation, \emph{FISEB/ILANIT}, Eilat. \\*[0.1cm]
\\*
2016
& Seminar, the \emph{Instituto Gulbenkian de Ci\^{e}ncia}, Portugal. \\*[0.1cm]
\\*
2015
& Oral presentation, \textbf{\emph{Gordon Research Conference}} on Biological Mechanisms in Evolution, Stonehill College, Easton, MA, USA \\*[0.1cm]
$\ast$ & Poster at the \emph{"Forecasting Evolution?"} SFB 680 conference in Lisbon, Portugal \\*[0.1cm]
$\ast$ & Seminar, \emph{Institute of Science and Technology}, Austria \\*[0.1cm]
$\ast$ & Short oral presentation, \emph{Two2Many} Systems Biology Conference, Weizmann Institute \\*[0.1cm]
\\
2013 
& Poster, \emph{ESEB 2013} in Lisbon, Portugal \\*[0.1cm]
$\ast$ & Poster, \emph{Gordon Research Conference} on Biological Mechanisms in Evolution, Stonehill College, Easton, MA, USA \\*[0.1cm]
$\ast$ & Oral presentation, 5th Annual \emph{SIDEER Graduate Symposium}, Ben-Gurion University of the Negev, Sede-Boqer Campus \\*[0.1cm]
\\
2012
& Oral presentation, \emph{Genetics, Genomics, and Evolution}, Ben-Gurion University of the Negev. DOI: \href{http://doi.org/10.6084/m9.figshare.96049}{10.6084/m9.figshare.96049}. \\*[0.1cm]
$\ast$ &  Oral presentation, \textbf{\emph{PopGroup 45}} in Nottingham, UK. DOI: \href{http://doi.org/10.6084/m9.figshare.95939}{10.6084/m9.figshare.95939}. \\*[0.1cm]
\\
2011
& Poster, \emph{ESEB 2011} in Tubingen, Germany. F1000 Posters 2011, 2: 1484. \\*[0.1cm]
\\
2010
& Poster, \emph{SMBE 2010} in Lyon, France. \\*[0.1cm]
as undergrad
& Poster, \emph{MMSB} in Tel Aviv, Israel, 2010 -- \textbf{Best poster award}\\*[0.1cm]

\end{longtable}
} 

%\pagebreak

\section*{Other Academic Activities} {
\begin{longtable}{L!{\VRule}R}

\textbf{Service} & \\*
2019 & Program committee, \emph{First Meeting of the Israeli Society for Evolutionary Biology} \\*
2011-2014 & Co-organizer, \href{https://biomathsjctau.wordpress.com}{BioMath Student Journal Club}, Tel Aviv University \\*
\\

\textbf{Outreach} & \\
2019 & Mentoring at \emph{\href{https://djangogirls.org/raanana/}{DjangoGirls Ra`anana}} \\*
2017 & \emph{Dive into Scientific Python} | Oral presentation, DataTalks meetup, Herzliya | \href{https://www.youtube.com/watch?v=TaIhctLjILI}{YouTube} \\*
2016 & \emph{How to study evolution using Scientific Python} | Oral presentation, PyCon Israel , Tel Aviv | \href{http://www.youtube.com/watch?v=2w8Tv016Frw}{YouTube} \\*
2013 & \emph{Evolution and mutation in stressful times} | Oral presentation, The Evolution Series, Tel Aviv University Botanical Gardens | \href{https://speakerdeck.com/yoavram/bvlvtsyh-vmvttsyh-b-tvt-qh}{PDF} \\*
\\

\textbf{Popular Media} 
& Even-Tov, E., Obolski, U., Gueijman, A., \textbf{Ram, Y.}, Hadany, L. (2010) \emph{The Evolutionary Riddle of Sexual Reproduction}. Galileo, an Israeli journal for popular science: June, 32-41 \\*
\\

\textbf{Reviewer} & \\*
2011-- & PLOS Genetics \\*
& Proceeding of the Royal Society B \\*
& Evolution \\*
& Journal of Evolutionary Biology \\*
& PLOS ONE \\*
& Theoretical Population Biology \\*
& Integrative Zoology \\*
& Quarterly Review of Biology \\*
& ReScience \\*
& Israel Journal of Ecology \& Evolution \\*
\\

\end{longtable}
} 

\end{document}




